---
title: "caribouIK"
author: ""
date: "18 March 2020"
output: pdf_document
---

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

## R Markdown

R Markdown syntax allows R code, outputs, and figures to be rendered in the documentation.

For help writing in R Markdown, see http://rmarkdown.rstudio.com/.

# Usage

```{r module_usage}
library(SpaDES.core)

setPaths(modulePath = file.path(getwd(), "modules"),
         inputPath = checkPath(file.path(getwd(), "testingCaribouIK"), create = TRUE),
         cachePath = file.path(getwd(), "cache"),
         outputPath = checkPath(file.path(getwd(), "testingCaribouIK"), create = TRUE))

getPaths() # shows where the 4 relevant paths are

times <- list(start = 2011, end = 2100)

parameters <- list(
  "caribouIK" = list(
     "decidousSp" = c("Betu_Pap", "Popu_Tre", "Popu_Bal"),
     "predictionInterval" = 30,
     "subsetForModel" = 50
  )
)
modules <- list("caribouIK")
objects <- list()
inputs <- list()
outputs <- list()

mySim <- simInitAndSpades(times = times, params = parameters, modules = modules,
                 objects = objects, debug = 1)

```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams}
df_params <- moduleParams("caribouIK", "..")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("caribouIK", "path/to/modules/dir")` may be sufficient.

```{r moduleInputs}
df_inputs <- moduleInputs("caribouIK", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs}
df_outputs <- moduleOutputs("caribouIK", "..")
knitr::kable(df_outputs)
```

# Links to other modules

Describe any anticipated linkages to other modules.
